\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}

\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain}

\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}


\usepackage{listings}

% Enabling Javascript syntax highlight in code snippet - BEGIN 
% https://tex.stackexchange.com/questions/89574/language-option-supported-in-listings
\usepackage{color}
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\definecolor{darkgreen}{rgb}{0, .64, 0}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{darkgreen}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\lstset{
   language=JavaScript,
   extendedchars=true,
   basicstyle=\footnotesize\ttfamily,
   showstringspaces=false,
   showspaces=false,
   numbers=left,
   numberstyle=\footnotesize,
   numbersep=9pt,
   tabsize=2,
   breaklines=true,
   showtabs=false,
   captionpos=b
}
% Enabling Javascript syntax highlight in code snippet - END

\newcommand{\APIName}{Successorships}

\newcommand{\APIshort}{ships}

%opening
\title{Who is the next server? Enabling fault-tolerant local Webapps}

\author{Arthur Marques \qquad Felix Grund \qquad Paul Cernek}
\affiliation{
    \institution{University of British Columbia}
    \city{Vancouver} 
    \state{BC} 
  }

\begin{document}

\maketitle

\begin{abstract}
In the face of the growing domain of the Internet of Things, we are recently observing increased usage of applications that communicate with each other within the local network. This trend has been driven by the concept of zero-configuration networking that eliminates the burden of setup procedures. While applications native to specific operating systems and devices have traditionally been the common case, browser vendors are now trying to bring this idea to the Web: any Web application can start its own server and advertise a service in the local network. The service can then be discovered and used by any connected browser-capable device in the same network which provides offline availablility and privacy and saves traffic. Since in such scenarios, any device can become a Web server, we argue that such applications can provide good fault-tolerance capabilities because the server role can simply be transferred to a client if the application's state is replicated. In this paper, we introduce a JavaScript library for such zero-configuration Web applications that enables graceful recovery after server failure by handing over the server role to the "next" client. We evaluated our approach with a sample application and usage by 5 participants. The results show that our library recovers the system gracefully after an average of 3.5 seconds and that application state is well-preserved.
\end{abstract}

\input{sections/introduction}

\input{sections/background}

\input{sections/proposed_approach}

\input{sections/evaluation}

\input{sections/timeline}

\bibliographystyle{abbrv}
\bibliography{flyweb_paper}

\end{document}

